Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex

We used three metris to measure of task performance: time to completion, the number of factors used in the choice, and the number of candidates

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks overall, with DP (condition A) taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B (the web browser/Excel interface) ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find a interface use a significant predictor of task completion time. A comparison of times taken are visible in Figure \ref{fig:time}.

Although across trials, restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor either.

@@

\subsection{Condition A (DP)}
In the A condition, where participants used DataPalette to complete their tasks they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of DataPalette, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.

>>>>

We used three metrics to measure task performance: time to completion; the number of factors used in the choice; and the number of candidates evaluated.

\subsubsection{Efficiency: Time taken}
Participants spent an average of 8.9 minutes performing the tasks overall, with condition A (DataPalette) taking slightly less time ($M=8.7$min, $SD=1.79$) per trial than condition B (the web browser/Excel interface) ($M=9.0$min; $SD=1.44$).  An ANOVA test of time taken by interface condition blocking by participant did not find interface use a significant predictor of task completion time. A comparison of times taken are visible in Figure \ref{fig:time}.

Although across trials, the restaurant selection task took on average slightly less time ($M=8.8$min,$SD=1.58$) than the university trials ($M=8.9$min,$SD=1.66$), the aforementioned ANOVA test found task type to not be a significant predictor.

@@

\subsection{Condition A (DataPalette)}
In the A condition, where participants used DataPalette to complete their tasks, they used it to collate the data on-screen, and compare multiple values directly. About half of the observed users actually used the instance combination feature of DataPalette, with the other half able to successfully make decisions without using it. Those who tried to use it were largely successful, and were able to therefore use the global brush-highlighting to simultaneously compare different statistics. Most users instantly opened up all data sources into individual boxes, in order to determine which sources contained specific statistics. The result of this technique is that the users instantly filled their screen, and ran out of space for plots and maps.
